%\documentclass[pdf,12pt,report,strict]{SANDreport}
\documentclass{article}
\usepackage{subfigure}
\usepackage[latin1]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\author{P. Bachant, M. Wosnik, V. Neary}
\title{Test Plan: UNH RM2 Tow Tank Experiment}

%\SANDnum{NUMBER}		% e.g. \SANDnum{SAND2006-0420}
%\SANDprintDate{DATE}	% Month, year
%\SANDauthor{AUTHORS}	% One line, separated by commas

\begin{document}

\maketitle
%\tableofcontents

\section{Objectives}

\begin{enumerate}

	\item Acquire a Reynolds number independent dataset for the DOE RM2 cross-flow
	turbine.

		\begin{enumerate}
			\item Design and build an appropriate turbine model.
		
			\item Acquire full device performance curves at multiple $Re$, to attempt to
			find convergence.
		  
			\item Once convergence is found, acquire another performance curve at that
			Reynolds number $Re_0$.
		
			\item If possible, acquire a detailed wake flow map in the near-wake at
			$Re_0$ using acoustic Doppler velocimetry.
		\end{enumerate}
	
	\item Measure the effects of strut drag on RM2 performance.
	
	\begin{enumerate}
		\item Measure the parasitic torque from support struts by rotating the turbine
		in still water. \label{obj-parasitic_torque}
		
		\item Redo task \ref{obj-parasitic_torque} with cylindrical tubes slid over
		the struts to significantly increase drag.
		
		\item Acquire a performance curve at $Re_0$ with the high-drag struts. 
	\end{enumerate}
	
\end{enumerate}


\section{Turbine model}

The turbine is to be a 1:6 scale model of the DOE RM2 rotor.

\subsection{Geometric requirements}

Turbine geometry is to be scaled from the RM2 design report \cite{Barone2011}.

\begin{table}[ht]
\centering
\begin{tabular}{l|l|l}
   & Full-scale & Model (1:6) \\
\hline 
Diameter (m)   & 6.45 & 1.075 \\ 
Height (m)     & 4.84 & 0.807 \\ 
Blade root chord (m) & 0.400 & 0.067 \\ 
Blade tip chord (m)  & 0.240 & 0.040 \\ 
Blade profile & NACA 0021 & NACA 0021 \\ 
Blade mount & 1/2 chord & 1/2 chord \\ 
Blade pitch (deg.) & 0.0 & 0.0 \\ 
Strut profile & NACA 0021 & NACA 0021 \\ 
Strut chord (m) & 0.360 & 0.060 \\ 
Shaft diameter (m) &  &  \\ 
\end{tabular}
\caption{RM2 turbine geometric parameters.}
\end{table}

The shaft diameter has still not been chosen.


\section{Experimental setup}

Experiments will be performed in the UNH tow/wave tank. The turbine will be
mounted in a frame built from NACA 0020 struts, attached to the tow carriage by
four linear bearings, which transfer all streamwise force to a pair of S-beam
load cells. The turbine shaft RPM will be controlled by a servo motor system,
which allows prescription of the turbine tip speed ratio. The load torque will
be measured by an inline rotary torque transducer and a load cell mounted at a
fixed distance from the servo motor, providing a redundant measurement. Turbine
shaft angle will be measured using the servo drive's emulated encoder output,
set to $10^5$ counts per turbine shaft revolution. Carriage speed, and therefore
inflow velocity will be measured using a linear encoder with 10 $\mu$m
resolution.


\bibliography{../../../../../Library/Library}
\bibliographystyle{plain}

\end{document}